Haskell in Computational Biology

### 2013-05-28 hov-prevs.tex
build instructions
more code snippets

prevs preceders stateHat fj fi =
 internal [ edge score state (vee'' state pj pi)
          | state <- preceders
          , let pi = fi state
          , pj >= 0, pi >= 0
          , let score = transition (node pj) state stateHat
                        + emission (node pj) state (residue pi)
          ]
 where pj = fj stateHat

predUnless :: forall a . Enum a => a -> StateLabel -> StateLabel -> a
predUnless n don't_move s = if s == don't_move then n else pred n

>>>>

       prevs predecessors stateHat fj fi =
        internal [ edge score state (vee'' state pj pi)
                 | state <- predecessors
                 , let pi = fi state
                 , pj >= 0, pi >= 0
                 , let score = transition (node pj) state stateHat
                               + emission (node pj) state (residue pi)
                 ]
        where pj = fj stateHat
prevs :: [StateLabel] -> StateLabel
      -> (StateLabel -> NodeIndex) -> (StateLabel -> ResidueCount) -> a

### 2013-05-28 hov4.tex
more code snippets

vee' Ins (NC 0) i = intoInsZero i
vee' Mat (NC 1) i = intoMatOne i
vee' Del (NC 1) i = intoDelOne i
vee' stateHat j i =
  internal [ edge score state (vee'' state pj pi)
           | state <- preceders stateHat
           , let pi = case state of { Del -> i ; _ -> pred i }
           , pj >= 0, pi >= 0
           , let score = transition (node pj) state stateHat
                         + emission (node pj) state (residue pi)
           ]
  where pj = case stateHat of { Ins -> j ; _ -> pred j }

>>>>

vee' :: StateLabel -> NodeIndex -> ResidueCount -> a
vee' Del (NI 1) (RC 0) = leaf (transition (node 0) Mat Del)
vee' Ins (NI 0) (RC 0) = leaf (transition (node 0) Mat Ins)
vee' Mat (NI 1) (RC 0) = leaf (transition (node 0) Mat Mat)
vee' stateHat j i = 
  internal [ edge score state (vee'' state pj pi)
           | state <- preceders stateHat
           , let pi = predUnless i Del state
           , pj >= 0, pi >= 0
           , let score = transition (node pj) state stateHat
                         + emission (node pj) state (residue pi)
           ]
  where pj = predUnless j Ins stateHat
